---
title: "Step Model"
author: "강동원"
date: 2020-04-27
categories: ["R"]
tags: ["R Markdown", "step model"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1
 First divide the data into two pieces using 50:50 proportion: one for
training and the other for test. (Use the last four digit of your ID as the
seed number and use 50:50 proportion)
```{r}
mail<-read.csv('data/directmail.csv')
mail<-na.omit(mail)
table(is.na(mail))

nobs=nrow(mail)
set.seed(2059)
i=sample(1:nobs, round(nobs*0.5))
train=mail[i,]
test=mail[-i,]
nrow(train);nrow(test)
```


## 2
 Fit the (1) Full Logistic Regression, (2) Stepwise Logistic Regression.
```{r}
str(train)
full_model<-glm(RESPOND~AGE+BUY18+CLIMATE+FICO+INCOME+MARRIED+OWNHOME+GENDER,family='binomial',data=train)
step_model<-step(full_model, direction='both')
prob_pred1<-predict(full_model,newdata=test,type='response')
prob_pred2<-predict(step_model,newdata=test,type='response')
y_pred1<-as.numeric(prob_pred1>0.075)
y_pred2<-as.numeric(prob_pred2>0.075)
```


## 3
 Draw a (non-cumulative) Lift Chart using R for the test data (use %
Response as the Y-axis). (Do not use R packages)
```{r}
#Full-model
scored1<-cbind(prob_pred1,test$RESPOND)
order_sc1<-as.data.frame(scored1[order(-prob_pred1),])
colnames(order_sc1)[2]<-'respond'
n<-round(nrow(order_sc1)/10)
lvp1=c()
for(i in 1:10){
  n1<-1+n*(i-1);n2<-n*i
  lv<-order_sc1[n1:n2,]
  lvpercent<-length(which(lv$respond==1))/nrow(lv)*100
  lvp1[i]<-lvpercent
  assign(paste0('lv1_',i),lv)
}
plot(lvp1,type='o',main='Non-Cumulative Lift Chart',xlab='Decile',ylab='Response (%)')


#Step-model
scored2<-cbind(prob_pred2,test$RESPOND)
order_sc2<-as.data.frame(scored2[order(-prob_pred2),])
colnames(order_sc2)[2]<-'respond'
n<-round(nrow(order_sc2)/10)
lvp2=c()
for(i in 1:10){
  n1<-1+n*(i-1);n2<-n*i
  lv<-order_sc2[n1:n2,]
  lvpercent<-length(which(lv$respond==1))/nrow(lv)*100
  lvp2[i]<-lvpercent
  assign(paste0('lv2_',i),lv)
}
plot(lvp2,type='o',main='Non-Cumulative Lift Chart',xlab='Decile',ylab='Response (%)')
```


## 4
 Draw a (cumulative) Lift Chart using R for the test data (use %
Captured Response as the Y-axis). (Do not use R packages)
```{r}
#Full-model
lvp1c=c()
lv1<-list()
for(i in 1:10){
  n1<-1+n*(i-1);n2<-n*i
  lv<-order_sc1[1:n2,]
  lvpercent<-length(which(lv$respond==1))/length(which(order_sc1$respond==1))
  lvp1c[i]<-lvpercent
  lv1[i]<-list(order_sc1[n1:n2,])
}
plot(lvp1c,type='o',main='Cumulative Lift Chart',xlab='Decile',ylab='Response (%)')

#Step-model
lvp2c=c()
lv2<-list()
for(i in 1:10){
  n1<-1+n*(i-1);n2<-n*i
  lv<-order_sc2[1:n2,]
  lvpercent<-length(which(lv$respond==1))/length(which(order_sc2$respond==1))
  lvp2c[i]<-lvpercent
  lv2[i]<-list(order_sc2[n1:n2,])
}
plot(lvp2c,type='o',main='Cumulative Lift Chart',xlab='Decile',ylab='% Captured Response')
```


## 5
 Which model would you choose?
```{r}
num=1:10
par(mfrow=c(1,2))
plot(lvp1,type='o',main='Non-Cumulative Lift Chart',xlab='Decile',ylab='Response (%)')
lines(lvp2,col=2)
abline(lm(lvp1~num))
abline(lm(lvp2~num),col=2)
legend('topright',c('Full-model','Step-model'),col=c(1,2),lwd=2)
plot(lvp1c,type='o',main='Cumulative Lift Chart',xlab='Decile',ylab='% Captured Response')
lines(lvp2c,col=2)
abline(lm(lvp1c~num))
abline(lm(lvp2c~num),col=2)
legend('bottomright',c('Full-model','Step-model'),col=c(1,2),lwd=2)
```
 abline의 기울기가 거의 비슷하다. Decile 1~2구간에서는 Step-Model의 기울기가 더 크므로, 해당 모델을 선택하도록 한다.


## 6
 Using the model that you chose in #5, draw a (cumulative) Profit Chart
using R for the validation data under the following conditions.
    Fixed cost = $5,000
    Cost per mailing = $7
    Profit for each purchase = $100
NOTE: Calculate profits for the company (not for a person).
```{r}
profit<-c()
for(i in 1:10){
  n1<-1+n*(i-1);n2<-n*i
  lv<-order_sc2[1:n2,]
  income<-length(which(lv$respond==1))*100
  cost<-5000+7*nrow(lv)
  profit[i]<-income-cost
}
plot(profit,type='o',main='Cumulative Profit Chart')
```


## 7
 Suggest the proportion of ‘likely-to-buy’ customers to mail out the
mailings, using the result in #6.

 Decile 1 부터 증가하고 4에서 Response가 최대가 되므로 decile 4까지를 대상으로 하는 것이 적절하다.